%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\textbf{}%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------\texttt{}------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style
\usepackage{fontawesome5}
\usepackage{setspace}
\usepackage[left=0.75in,top=0.3in,right=0.75in,bottom=0.3in]{geometry} % Document margins
\usepackage{hyperref}
\usepackage{xcolor}
%\hypersetup{
%	colorlinks=true
%	linkcolor=blue;
%	filecolor=magenta;      
%	urlcolor=cyan;
%}

\urlstyle{same}

\name{Travis Brown} % Your name
\address{   \quad \faPhone* (386) 631-7437 \quad \\ \quad {\color{cyan} \href{https://www.linkedin.com/in/travis-brown-a9887019a/}{\faLinkedin \enspace LinkedIn}}\quad \\ \quad {\href{https://github.com/TravisB1231}{\faGithub \enspace TravisB1231}} \quad \\ \quad \faMailBulk TravisRBrown1231@gmail.com }
\begin{document}
	\begin{center}{\vspace{-0.1cm}A lifelong learner with a commitment to curiosity, empathy, automation, \& security.\vspace{-0.1cm}}\end{center}
{\small
	%----------------------------------------------------------------------------------------
	%	WORK EXPERIENCE SECTION
	%----------------------------------------------------------------------------------------
	\setstretch{1.2}
	\vspace{-0.2cm}
	\begin{rSection}{Employment}
		\vspace{-0.2cm}
		{\bf Rapid7} - {\em Support Engineer} \hfill {\em December 2021 - Present}\\
		Unix, cloud, \& container security, \& API integration support for 10,000+ customers. 
		\begin{itemize}
			\vspace{-0.2cm} \item AWS cloud admin for support org - drove a 70\% cost reduction with Boto3 \& Terraform.
			\vspace{-0.2cm} \item Create REST API testing \& automation scripts using Python \& Docker.
			\vspace{-0.2cm} \item InsightVM focus - Unix, Windows, network, database vulnerability \& policy assessment.
			\vspace{-0.2cm} \item API integration specialist - AWS, Docker, Kubernetes, Jenkins, Jira, ServiceNow, splunk, \& more.
			\vspace{-0.2cm} \item Container image assessment via InsightVM's registry scanning \& Jenkins CI/CD plugin.
			\vspace{-0.2cm} \item InsightAppSec cross-training - DAST, authentication, \& Jenkins CI/CD integration.
			%\vspace{-0.2cm} \item Presented on engineer workflow \& Docker enablement.
			\vspace{-0.2cm} \item Mentor for Rapid7 internship program.
			\setstretch{1.2}
		\end{itemize}
		\setstretch{1.2}
		{\bf Florida Department of Agriculture} - {\em Support Analyst} \hfill {\em July 2021 - December 2021}\\
		\setstretch{1.25}
		Desktop support for an enterprise of 4,500+ users.
		
		%\begin{itemize}
			%\vspace{-0.2cm} \item Created security awareness training scenarios.
		%\end{itemize}
		\setstretch{1.25}
		{\bf Florida State University} - {\em Support Analyst} \hfill {\em January 2020 – July 2021} \\
		\setstretch{1.2}
		Sysadmin, security for Windows \& RHEL servers, level 2 desktop support for 500+ users.
		\begin{itemize}
			\vspace{-0.2cm} \item Implemented CIS Windows 10 Workstation L1 hardening benchmarks using GPO \& PowerShell.
			\vspace{-0.2cm} \item Tightened security posture, vulnerability assessment with InsightVM.
			%\vspace{-0.2cm} \item Sysadmin for 13 Windows servers, 1 RHEL server.
			\vspace{-0.2cm} \item Audited server \& network infrastructure (weak configurations, cipher suites).
			\vspace{-0.2cm} \item Automated remediation for RHEL, MacOS, \& Windows via Bash, Python, Munki, GPO, PowerShell.
			%\vspace{-0.2cm} \item Segmented network into more secure subnets.
			%\vspace{-0.2cm} \item Designed webpages in Drupal \& Bootstrap for the College's official website. % {\color{cyan} \href{https://music.fsu.edu/ensembles/orchestras/audition-information-orchestras}{website}}.
		\end{itemize}
		{\bf Arcvale Entertainment} - {\em Engineering Intern, Unity} \hfill {\em November 2019 – June 2020}\\
		DevOps Evangelist. Software engineering intern for an upcoming Nintendo Switch release.
		\begin{itemize}
			\vspace{-0.2cm} \item Reviewed, refactored, designed, \& authored code in C\#.
			\vspace{-0.2cm} \item GitLab maintainer. Provisioned, monitored, secured GitLab infrastructure.
			\vspace{-0.2cm} \item Implemented linting, unit testing, \& merge automation with GitLab Runners.
			%\vspace{-0.2cm} \item Evangelized DevOps \& GitOps principles.
		\end{itemize}
	\vspace{-3ex}
	\end{rSection}
		%----------------------------------------------------------------------------------------
		%	SKILLS SECTION
		%----------------------------------------------------------------------------------------
		\begin{rSection}{Skills}
			\setstretch{1.35}
			\begin{center}
				\vspace{-0.1cm}$\diamond$ {\bf Dev }$\diamond$ \\
				Python $\mid$ Bash $\mid$ Terraform $\mid$ Git $\mid$ REST APIs $\mid$ Jenkins $\mid$ CI/CD $\mid$ OOP $\mid$ NoSQL $\mid$ PostgreSQL\\
				
				$\diamond$ {\bf Sec} $\diamond$ \\
				Vulnerability assessment $\mid$ DAST $\mid$ Container image scanning $\mid$ Configuration management
				\\CIS benchmarks $\mid$ Nmap $\mid$ Wireshark $\mid$  TLS \& PKI $\mid$ Cryptography $\mid$ Least privilege\\
				
				$\diamond$ {\bf Ops} $\diamond$ \\
				Linux $\mid$ Docker $\mid$ TCP/IP $\mid$ DNS $\mid$ HTTP $\mid$ Network troubleshooting  $\mid$ LDAP/AD $\mid$ Deployment strategies\\
				
				$\diamond$ {\bf AWS} $\diamond$ \\ IAM $\mid$ Boto3 $\mid$ Lambda $\mid$ DynamoDB $\mid$ S3 $\mid$ RDS $\mid$ API Gateway $\mid$ SQS $\mid$ SNS $\mid$ CloudFormation $\mid$ Code*\\ EC2 $\mid$ ECS $\mid$ Fargate $\mid$ ASGs $\mid$ ELBs $\mid$ VPC $\mid$ CloudFront $\mid$ Route 53 $\mid$ CloudTrail $\mid$ Eventbridge $\mid$ CloudWatch  \\
				
				$\diamond$ {\bf Soft Skills} $\diamond$ \\
				Troubleshooting $\mid$ Excellent communication $\mid$ Public speaking $\mid$ Leadership $\mid$ Mentoring\\
			\end{center}
			\setstretch{1.25}
			%{\bf Studying}\\
			%AWS Certified DevOps Engineer - Professional\\
			%HashiCorp Certified Terraform Associate
			%Red Hat Certified Systems Administrator
			%\textbf{Languages}\\
			%Bash; Python; %CSS (Bootstrap); HTML;
			%\textbf{Platforms}\\
			%AWS; Docker; Linux; Windows;
			% \textbf{Regulations}\\
			% FERPA; GDPR; HIPAA;
			%\textbf{Tools}\\
			%Active Directory; InsightVM; Jira; nmap; openssl; Wireshark;
			%\textbf{Knowledge}\\
			%API scripting; Cloud \& network security; Containers; DNS; Git; Networking; Object-oriented Programming; TCP/IP; TLS/SSL; Troubleshooting; Vulnerability management;
			\vspace{-2ex}
		\end{rSection}
	%----------------------------------------------------------------------------------------
	%	EDUCATION SECTION
	%----------------------------------------------------------------------------------------
	\begin{rSection}{Education}
		\setstretch{1.25}
		\vspace{-0.2cm}
		{\bf \quad \quad \quad \quad \quad Certifications} \hfill {\bf Studying \quad \quad \quad \quad \quad \quad}\hfill \\
		%{\color{cyan}
			%\href{https://www.credly.com/badges/ID}
			%{\em Cert Name}} \hfill {\em Date}\\
		{\color{cyan}
			\href{https://www.credly.com/badges/b9878dcd-04a3-477f-85fc-27daa383e4de}
			{\em AWS Certified Developer - Associate}} \hfill HashiCorp Certified Terraform Associate\\ %\hfill {\em October 2022}\\
		{\color{cyan}
			\href{https://www.credly.com/badges/e2e9fabd-695d-4bb0-aa74-737fbebd64c9}
			{\em AWS Solutions Architect - Associate}} \hfill AWS Certified DevOps Engineer - Professional \\ %\hfill{\em August 2022}\\
		{\color{cyan}
			\href{https://www.credly.com/badges/fb3524b2-ef52-4c7b-9854-e00dd92e7046}
			{\em CompTIA Security+}}\\ %\hfill {\em September 2021}\\
		{\color{cyan}
			\href{https://verify.skilljar.com/c/sxetfkgywaqn}
			{\em InsightVM Certified Administrator}}%\hfill {\em January 2022}
		\begin{center}
			{\bf Florida State University}\\ %\hfill {\em Graduated May 2020} \\
			Music Liberal Studies B.A. - Computer Science \& IT Minors\end{center}
		\vspace{-0.2cm}\rule{\textwidth}{0.5pt}
	\end{rSection}

	%----------------------------------------------------------------------------------------
	%	Current Projects SECTION
	%----------------------------------------------------------------------------------------
	\begin{rSection}{Projects}
		\setstretch{1.1}
		{\bf Containerized multi-threaded API testing script}\\
		Container image to run a multi-threaded InsightVM API testing Python script. All made from scratch using Python's concurrent.futures module \& Docker.\\
		
		{\bf AWS Boto3 module/class design}\\
		Reusable modules for Boto3 authentication \& streamlining the JSON data received from various AWS services.\\
		
		{\bf AWS Boto3 EC2 automation scripts}\\
		Using the above modules, quickly created scripts for EBS volume checking, EC2 instance tagging, \& Lambda functions to shutdown instances based on tags. Automated with Eventbridge chron events.\\
		
		{\bf Terraform AWS deployments}\\
		Various infrastructure including VPCs, subnets, ELBs, EC2 instances, ASGs, IAM resources, secure S3 buckets, encrypted RDS/Aurora databases with enforced TLS connections, deployed with Terraform.\\
		
		{\bf AWS Boto3 \& Terraform - Checking EC2 Instance Profile permissions (WIP)}\\
		Boto3 script to check a region's EC2 instance profiles, then parse each role's JSON IAM policy documents to check if it can write to a specific S3 bucket. Written using Boto3.
		S3 buckets, IAM policies, IAM roles, VPCs, EC2 instances, EC2 instance profile associations created with Terraform.\\
		
		{\bf GitLab with GitLab Runners}\\
		Self-managed GitLab server for a Unity C\# project. GitLab Runners conducted unit testing to validate functionality before integration, \& linting to minimize diffs. Deployed on Ubuntu within AWS, monitored with CloudWatch.\\
		
		{\bf Jenkins pipeline with DAST}\\
		Docker-hosted Jenkins pipeline using GitHub APIs \& the InsightAppSec plugin for DAST.\\
		
		%{\bf Jenkins pipeline for creative project (WIP)}\\
		%VPCs, EC2 instances, IAM resources, encrypted S3 buckets deployed with Terraform.\\
		
		{\bf Learning K8s microservices (WIP)}\\
		Local minikube Kubernetes cluster deployed using Docker as the container runtime. Simple authentication, queues, \& databases to mirror a proper microservice architecture. Built with Python, MySQL, MongoDB, \& RabbitMQ. Managed with k9s.\\
				
		{\bf Collaborative chaos engineering \& response}\\
		A group of friends each maintaining \& monitoring their own RHEL httpd servers in their own AWS accounts. Each has remote access to the others' servers \& does what they can to randomly antagonize, stress, or break each others' environments.\\
		
		\vfill\rule{\textwidth}{0.5pt}
	\end{rSection}
	
	%----------------------------------------------------------------------------------------
	}
\end{document}
